Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-29 thesis/experiment.tex
Add number of packets and fix size in bytes

\begin{table}[H]
  \begin{tabular}{lrr}
    \toprule
    Phase & Size in bytes & Number of sessions\\
    \midrule
    HTTPS & 2326328 & 236659\\
    HTTP over Tor & 2869624 & 168876\\
    HTTPS over Tor & 1591112 & 95203\\
    \bottomrule
    \label{table:datasets}
  \end{tabular}
  \caption{Captured Data}
\end{table}

>>>>

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    Phase & Size in bytes & Number of packets & Number of sessions\\
    \midrule
    HTTPS & 10,225,257,319 & 11,883,703 & 236,659\\
    HTTP over Tor & 11,270,515,232 & 14,823,849 & 168,876\\
    HTTPS over Tor & 5,988,282,097 & 8,161,620 & 95,203\\
    \bottomrule
    \label{table:datasets}
  \end{tabular}
  \caption{Captured Data}
\end{table}
